\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{array}
\usepackage{gensymb}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[table,xcdraw]{xcolor}
\usepackage{tabularx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
	
	\title{Classification of Fruits and Vegetables on a Conveyor}
		\author{\IEEEauthorblockN{Arvind Suresh}
		\and
		\IEEEauthorblockN{Sriram Suresh}
		\and
		\IEEEauthorblockN{Enoch Ramesh}
	}
	
	\maketitle
	
	\begin{abstract}
		This document is a model and instructions for \LaTeX.
		This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
		or Math in Paper Title or Abstract.
	\end{abstract}
	
	\begin{IEEEkeywords}
		component, formatting, style, styling, insert
	\end{IEEEkeywords}
	
	\section{Introduction}
	\input{./subsections/intro}
	
	\section{Related Literature}
	\input{./subsections/related_literature}
	
	\section{Data Acquisition}
	\input{./subsections/data_acquisition}
	
	\section{Image Preprocessing}
	\input{./subsections/image_preprocessing}
	
	\section{Classifiers} \label{classifiers}
	
	\begin{thebibliography}{00}
		\bibitem{b1_1} J. Fan and L. Gao, ``Vegetables logistics informationize in supply chain,'' in 2014 9th IEEE Conference on Industrial Electronics and Applications, 2014.
		\bibitem{b1_2} V. Réquillart, M. Simioni, and X.L. Varela-Irimia, ``Imperfect Competition in the Fresh Fruit and Vegetable Industry'', European Association of Agricultural Economists, 113th Seminar, Sept. 2009.
		\bibitem{b1_3} ``Environmental Guidelines for Fruit and Vegetable Processing.'' [Online]. Available: https://www.miga.org/sites/default/files/ archive/Documents/FruitandVegetableProcessing.pdf.
		\bibitem{b1_4} ``Use Of Food Conveyor Belts In Food Handling Conveyors,'' Alpha Conveyor. [Online]. Available: https://www.alphaconveyor.com/products/food-grade-conveyor/use-of-food-conveyor-belts-in-food-handling-conveyors/.
		\bibitem{b1_5} A. Ren, Z. Li, C. Ding, Q. Qiu, Y. Wang, J. Li, X. Qian, and B. Yuan, ``Sc-dcnn: Highly-scalable deep convolutional neural network using stochastic computing'', Proceedings of the Twenty-Second International Conference on Architectural Support for Programming Languages and Operating Systems, pp. 405-418, 2017.
		\bibitem{b1_6} Z. Li, A. Ren, J. Li, Q. Qiu, B. Yuan, J. Draper, and Y. Wang, ``Structural design optimization for deep convolutional neural networks using stochastic computing'', 2017 Design Automation \& Test in Europe Conference \& Exhibition (DATE), pp. 250-253, 2017.
		\bibitem{b1_7} K. Simonyan and A. Zisserman, ``Very deep convolutional networks for large-scale image recognition,'' 2014.
		\bibitem{b1_8} G.-B. Huang, Q.-Y. Zhu, and C.-K. Siew,``Extreme learning machine: theory and applications'', Neurocomputing, vol. 70, no. 1, pp. 489-501, 2006.
		\bibitem{b2_1} Yu Haiyang, Liu Yanmei, Yang Guijun, and Yang Xiaodong, ``Quick image processing method of HJ satellites applied in agriculture monitoring,'' in 2016 World Automation Congress (WAC), 2016.
		\bibitem{b2_2} M. Sato, S.-W. Chen, and M. Satake, ``Polarimetric SAR analysis of tsunami damage following the March 11 2011 East Japan Earthquake'', Proc. IEEE, vol. 100, no. 10, pp. 2861-2875, Oct, 2012.
		\bibitem{b2_3} S.-W. Chen and M. Sato, ``Tsunami damage investigation of built-up areas using multitemporal spaceborne full polarimetric SAR image'', IEEE Trans. Geosci. Remote Sens., vol. 51, no. 4, pp. 1985-1997, Apr. 2013.
		\bibitem{b2_4} S. W. Chen, X. S. Wang, and M. Sato, ``Urban damage level mapping based on scattering mechanism investigation using fully polarimetric SAR data for the 3.11 East Japan earthquake'', IEEE Trans. Geosci. Remote Sens., vol. 54, no. 12, pp. 6919-6929, 2016.
		\bibitem{b2_5} J. M. Lopez-Sanchez, F. Vicente-Guijalba, J. D. Ballester-Berman, and S. R. Cloude, ``Polarimetric response of rice fields at C-band: Analysis and phenology retrieva'', IEEE Trans. Geosci. Remote Sens., vol. 52, no. 5, pp. 2977-2993, May 2014.
		\bibitem{b2_6} C. Yonezawa, M. Negishi, K. Azuma, M. Watanabe, N. Ishitsuka, S. Ogawa, and G. Saito, ``Growth monitoring and classification of rice fields using multitemporal RADARSAT-2 full-polarimetric data'', Int. J. Remote Sens., vol. 33, no. 18, pp. 5696-5711, 2012.
		\bibitem{b2_7} S.-W. Chen and C.-S. Tao, ``Multi-temporal PolSAR crops classification using polarimetric-feature-driven deep convolutional neural network,'' in 2017 International Workshop on Remote Sensing with Intelligent Processing (RSIP), 2017.
		\bibitem{b2_8} J. Gill, P.S. Sandhu, and T. Singh, ``A Review of Automatic Fruit Classification using Soft Computing Techniques'', International Conference on Computer Systems and Electronics Engineering (ICSCEE'2014), pp. 91-98, 2014.
		\bibitem{b2_9} M. Raj and D. Swaminarayan, ``Applications of Image Processing for Grading Agriculture products'', International Journal on Recent and Innovation Trends in Computing and Communication, vol. 3, no. 3, pp. 1194-1201, 2015.
		\bibitem{b2_10} S. Banot and P.M. Mahajan, ``A Fruit Detecting and Grading System Based on Image Processing-Review'', International Journal of Innovative Research in Electrical Electoronics Instrumentation and Control Engineering, vol. 4, no. 1, 2016.
		\bibitem{b2_11} R. Socher, B. Huval, B. Bhat, C.D. Manning, and A.Y. Ng, ``Convolutional-Recursive Deep Learning for 3D Object Classification'', Advances in Neural Information Processing Systems 25 (NIPS 2012), 2012.
		\bibitem{b2_12} A. Eitel, J.T. Springenberg, L. Spinello, M. Riedmiller, and W. Burgard, ``Multimodal Deep Learning for Robust RGB-D Object Recognition'', IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), 2015.
		\bibitem{b2_13} T. Nishi, S. Kurogi, and K. Matsuo, ``Grading fruits and vegetables using RGB-D images and convolutional neural network,'' in 2017 IEEE Symposium Series on Computational Intelligence (SSCI), 2017.
		\bibitem{b2_14} ``How a Japanese cucumber farmer is using deep learning and TensorFlow,'' Google Cloud Blog. [Online]. Available: https://cloud.google.com/blog/products/gcp/how-a-japanese-cucumber-farmer-is-using-deep-learning-and-tensorflow.
		\bibitem{b2_15} Y. Sakai, T. Oda, M. Ikeda, and L. Barolli, ``A Vegetable Category Recognition System Using Deep Neural Network,'' in 2016 10th International Conference on Innovative Mobile and Internet Services in Ubiquitous Computing (IMIS), 2016.
		\bibitem{b2_16} O. Patil, ``Classification of Vegetables using TensorFlow,'' International Journal for Research in Applied Science and Engineering Technology, vol. 6, no. 4, pp. 2926–2934, Apr. 2018.
		\bibitem{b2_17} A. B. Titus, T. Narayanan, and G. P. Das, ``Vision system for coconut farm cable robot,'' in 2017 IEEE International Conference on Smart Technologies and Management for Computing, Communication, Controls, Energy and Materials (ICSTM), 2017.
		\bibitem{b2_18} Shweta A.S, ``Intelligent refrigerator using ARTIFICIAL INTELLIGENCE,'' in 2017 11th International Conference on Intelligent Systems and Control (ISCO), 2017.
		\bibitem{b2_19} H.-L. Kuang, L. L. H. Chan, and H. Yan, ``Multi-class fruit detection based on multiple color channels,'' in 2015 International Conference on Wavelet Analysis and Pattern Recognition (ICWAPR), 2015.
		\bibitem{b2_20} N. Kulu, M. Baskaya, A. Keles, A. Altan, and R. Hacioglu, ``Determination of Fruit Health Status and Yield with Unmanned Aerial Vehicle,'' in 2018 2nd International Symposium on Multidisciplinary Studies and Innovative Technologies (ISMSIT), 2018.
		\bibitem{b3_1} R. S. Berns and D. M. Reiman, ``Color managing the third edition ofBillmeyer and Saltzman’s Principles of Color Technology,'' Color Research \& Application, vol. 27, no. 5, pp. 360–373, Aug. 2002.
		\bibitem{b4_1} Y. Li, J. Zhang, P. Gao, L. Jiang, and M. Chen, ``Grab Cut Image Segmentation Based on Image Region,'' in 2018 IEEE 3rd International Conference on Image, Vision and Computing (ICIVC), 2018.
		\bibitem{b4_2} M. Mustra, ``Creating Segmentation Masks for Benchmark in Digital Mammography,'' in 2018 Zooming Innovation in Consumer Technologies Conference (ZINC), 2018.
		\bibitem{b4_3} Sheng Yan, Jianping Yuan, and Chaohuan Hou, ``Segmentation of medical ultrasound images based on level set method with edge representing mask,'' in 2010 3rd International Conference on Advanced Computer Theory and Engineering(ICACTE), 2010.
		\bibitem{b4_4} H. M. Zawbaa, M. Hazman, M. Abbass, and A. E. Hassanien, ``Automatic fruit classification using random forest algorithm,'' in 2014 14th International Conference on Hybrid Intelligent Systems, 2014.
	\end{thebibliography}
\end{document}
